\documentclass[letterpaper,11pt]{article}

%-------------------- PACKAGES --------------------
\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{graphicx}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

%-------------------- MARGINS --------------------
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

%-------------------- SECTION FORMATTING --------------------
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%==================== CUSTOM COMMANDS ====================

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\seticon}[1]{\textcolor{Black}{\csname #1\endcsname}}

%==================== DOCUMENT ====================

\begin{document}

%-------------------- HEADING --------------------
\begin{center}
    \textbf{\Huge \scshape Arjun Mehta} \\ \vspace{1pt}
    \seticon{faPhone} \ \small +91-98XXXXXXX \quad
    \href{mailto:arjun.mehta.ai@gmail.com}{\seticon{faEnvelope} \underline{arjun.mehta.ai@gmail.com}} \quad
    \href{https://www.linkedin.com/in/arjunmehta-ai}{\seticon{faLinkedin} \underline{linkedin.com/in/arjunmehta-ai}} \quad
    \href{https://github.com/arjunmehta-ai}{\seticon{faGithub} \underline{github.com/arjunmehta-ai}}
\end{center}

%-------------------- SUMMARY --------------------
\section{Summary}
\small{
AI/ML Engineer with 5+ years of experience designing, training, and deploying machine learning systems in production. Strong background in deep learning, NLP, and large-scale data pipelines, with hands-on experience shipping models end-to-end — from research and experimentation to scalable inference. Adept at translating business problems into measurable ML objectives and building systems that balance accuracy, latency, and reliability.
}

%-------------------- EDUCATION --------------------
\section{Education}
\resumeSubHeadingListStart

    \resumeSubheading
    {Indian Institute of Technology (IIT)}{Delhi, India}
    {Bachelor of Technology in Computer Science and Engineering}{Jul 2015 -- May 2019}
    \resumeItemListStart
        \resumeItem{Graduated with Distinction; GPA: 8.9/10}
        \resumeItem{Relevant Coursework: Machine Learning, Deep Learning, Probability, Algorithms, Distributed Systems}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- EXPERIENCE --------------------
\section{Experience}
\resumeSubHeadingListStart

    \resumeSubheading
    {Senior AI/ML Engineer}{Aug 2022 -- Present}
    {FinTech Scale-up}{Bangalore, India}
    \resumeItemListStart
        \resumeItem{Designed and deployed fraud detection models using gradient boosting and deep neural networks, reducing fraudulent transactions by 38\% at constant false-positive rates.}
        \resumeItem{Built real-time inference pipelines using FastAPI, Redis, and Kafka, achieving sub-50ms latency at peak traffic.}
        \resumeItem{Led model evaluation strategy, introducing offline metrics, shadow deployments, and A/B testing for reliable production rollouts.}
        \resumeItem{Mentored junior engineers on ML system design, feature engineering, and production debugging.}
    \resumeItemListEnd
    
    \resumeSubheading
    {Machine Learning Engineer}{Jul 2019 -- Jul 2022}
    {AI Products Company}{Hyderabad, India}
    \resumeItemListStart
        \resumeItem{Developed NLP models for document classification and information extraction using BERT-based architectures, improving accuracy by 22\%.}
        \resumeItem{Implemented automated training pipelines using PyTorch, MLflow, and Airflow to support continuous model iteration.}
        \resumeItem{Collaborated with product and backend teams to integrate ML outputs into customer-facing features.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- PROJECTS --------------------
\section{Projects}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{LLM-powered Knowledge Assistant} $|$ \emph{Python, LangChain, FAISS, OpenAI}}{2024}
    \resumeItemListStart
        \resumeItem{Built a retrieval-augmented generation (RAG) system for internal knowledge search across 1M+ documents.}
        \resumeItem{Implemented chunking, embeddings, and re-ranking strategies to improve answer relevance by 30\%.}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{Real-time Recommendation Engine} $|$ \emph{PyTorch, Kafka, Redis}}{2023}
    \resumeItemListStart
        \resumeItem{Designed a hybrid collaborative-filtering and content-based recommendation system for personalized user feeds.}
        \resumeItem{Scaled inference to handle 10K+ requests per second with horizontal scaling.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
\small{
    \item{
        \textbf{Languages}{: Python, C++, SQL, Bash} \\
        \textbf{ML / AI}{: PyTorch, TensorFlow, Scikit-learn, Transformers, NLP, LLMs} \\
        \textbf{Data \& Systems}{: Kafka, Redis, Airflow, Spark, Docker, Kubernetes} \\
        \textbf{MLOps}{: MLflow, Model Monitoring, A/B Testing, CI/CD for ML}
    }
}
\end{itemize}

%-------------------- PUBLICATIONS --------------------
\section{Publications}
\resumeSubHeadingListStart

    \item \small{
    Mehta, A., Sharma, R. \textit{Efficient Feature Learning for Transaction Fraud Detection}.  
    IEEE International Conference on Data Mining (ICDM), 2022.
    }

    \item \small{
    Mehta, A. \textit{Scalable NLP Pipelines for Enterprise Document Intelligence}.  
    ACM Workshop on Applied Machine Learning, 2021.
    }

\resumeSubHeadingListEnd

\end{document}
